\plaintitle

### 2017-06-16 papers/IoT2017/intro.tex
updates

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. % \cite{EIA2014}
For example, 
$4,\!143$ megawatts of solar panels were installed in the third quarter of 2016 \cite{seia}. This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time, battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity. % \cite{bronski2015economics}
This massive integration of renewable energy requires detailed information and visibility into all aspects of the network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}. Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}. In this vision, energy generation, transmission, distribution and even storage (e.g., electric vehicles in a community) can be strategically used to balance load and demand spikes.

Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}. In this approach, customers on the same feeder (i.e. sharing a power line link) can operate in an open market, trading and exchanging generated energy locally. Distribution System Operators (DSO) can be the custodian of this market, while still meeting the net demand \cite{7462854}. For example, the Brooklyn Microgrid, which was developed by LO3 Energy as a pilot project, is a peer-to-peer market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

On one hand, transactive energy is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control to maintain the stability of the community and the utility. On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system. However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges. 
Recently, demand-response systems have been enabled as applications of IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are the next step for smart grid.
% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.

In general, the focus is now on creating a distributed IoT infrastructure%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
, which provides the necessary computation fabric to support the interplay between energy control and fiscal market challenges, as shown by Volttron \cite{katipamula2016volttron},  OpenFMB \cite{gunthersmart}, and the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a distributed IoT  ``operating system'' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security. However, most of these efforts are focusing on the computation and distribution of information and, and they do not provide the key support required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.

In this paper, we assume the existence of the IoT infrastructure and specifically focus on the following privacy challenges.
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the operator. 
\item Secondly, \Abhishek{Is this not related to the first point? Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information. I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (or past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer sources of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy system can be deployed in practice, we must address these privacy issues.
However, this is a challenging task, as the system also has to satisfy security and safety requirements, which often conflict with privacy goals.
For example, to prevent a prosumer from destabilizing the grid through careless of malicious energy trading, the system must check all of the prosumer's transactions.
In a decentralized system, this requires disseminating information, which could be used to infer the prosumer's future energy consumption.

\Abhishek{Can we cite an example of such a service?}
\Aron{I am not sure what you mean by ``such a service.''}
\Abhishek{We should connect the paper and our work back to IoT in this paragraph.}
In this paper, we propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
First, we describe the basic components of a transactive IoT microgrid, and we formulate security, safety, and privacy requirements. 
Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
Next, we discuss how the system satisfies the security, safety, and privacy requirements.
Finally, we give a brief overview of related work and offer concluding remarks.

>>>>

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
%\cite{bronski2015economics}
This massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\em{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, customers on the same
feeder (\em{i.e.}, those sharing a power line link) can operate in an
open market, trading and exchanging generated energy
locally. Distribution System Operators (DSOs) can be the custodian of
this market, while still meeting the net demand \cite{7462854}. For
example, the Brooklyn Microgrid, which was developed by LO3 Energy as
a pilot project, is a peer-to-peer market for locally generated
renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
the next step for the smart grid.
% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.

In general, the focus is now on creating a distributed IoT
infrastructure
%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
that provides the necessary computation fabric to support the
interplay between energy control and fiscal market challenges, as
shown by Volttron \cite{katipamula2016volttron}, OpenFMB
\cite{gunthersmart}, and the Resilient Information Architecture
Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
distributed IoT operating system that provides the foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security. Most of these efforts, however, focus on the
computation and distribution of information, but do not provide the
support required to handle the privacy challenges that arise from the
required information exchange in this decentralized transactive
system.

This paper assumes the existence of a distributed IoT infrastructure
and specifically focus on the following privacy challenges:
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
% Abhishek, can you please add a pithy summary of this challenge?
\item \bf{Pithy challenge summary needed.} Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

% Abhishek, can you please add a pithy summary of this challenge?
\item \bf{Pithy challenge summary needed.} \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\em{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later, which could be a security risk.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play a important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

% Abhishek, can you please add a pithy summary of this challenge?
\item \bf{Pithy challenge summary needed.} Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple energy usage data collected by smart
  meters.  More specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy system can be deployed widely in practice,
we must address the privacy issues described above.  Addressing these
issues is hard, however, since solutions also must satisfy security
and safety requirements, which often conflict with privacy goals.  For
example, to prevent a prosumer from destabilizing the grid through
careless of malicious energy trading, the system must check all of the
prosumer's transactions.  In a decentralized system, this requires
disseminating information, which could be used to infer the prosumer's
future energy consumption.

\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
  sure what you mean by ``such a service.''}  \Abhishek{We should
  connect the paper and our work back to IoT in this paragraph.}  This
paper proposes a solution that (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules.  \Aron{Since SIGCHI does not have section numbers, this
  paragraph, which describes the organization of the paper, is not
  very clear.}  We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  We next introduce a decentralized system for
transactive microgrids based on distributed ledgers and describe the
transactions and services used to implement this system.  We then
discuss how the system satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

### 2017-06-16 papers/IoT2017/paper.tex
updates

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also create significant management challenges as the complexity of power systems increases.
To tackle these challenges, decentralized IoT solutions are emerging, which may arrange local communities into transactive microgrids.
Within a transactive microgrid, consumers with energy generation and storage capabilities can trade energy with each other, thereby smoothing the load on the main grid using local supply.
However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
On the one hand, consumers' personal information must be protected from their trade partners and
\Abhishek{To what extent is this different that the information already known by the system operator? Is this more related to the ``real-time'' nature of transactive information? Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?}\Abhishek{we dont have to} the system operator.
On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 
In this paper, we design a secure and safe solution for transactive microgrids, which enables consumers to trade energy without sacrificing their privacy.
Our solution builds on distributed ledgers, such as blockchains, and provides anonymity for communication, bidding, and trading.
\end{abstract}

>>>>

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply.  It is hard, however, to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and \Abhishek{To what extent is
  this different that the information already known by the system
  operator? Is this more related to the ``real-time'' nature of
  transactive information?  Rather than aggregative total information
  which is available at the end of billing cycle today.} \Aron{Do we
  need to detail this in the abstract?}\Abhishek{we dont have to} the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes our secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  Our solution builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}
